---
title: "readme"
output: github_document
---

## Summary:

Just playing around with different methods in generating uuid v4 in R. Comparing different benchmarks 

* Rcpp implementation based off: https://github.com/rkg82/uuid-v4
* package uuid: https://github.com/s-u/uuid
* package uwu: https://github.com/JosiahParry/uwu
* Base R implementation based off c++ implementation: https://github.com/rkg82/uuid-v4

```{r setup, include=F}
source("R/uuid.R")
Rcpp::sourceCpp("src/uuid.cpp")
```


## Benchmark:

Initially compare base R implementations.

```{r atime_base}
subject.size.vec <- unique(as.integer(10^seq(0,6,l=100)))
atime.list <- atime::atime(
  N = subject.size.vec,
  base_loop = uuid_v4_base_loop(N),
  base_vector = uuid_v4_base_vector(N)
)

atime.list
plot(atime.list)
## Compute and plot asymptotic reference lines:
best.list <- atime::references_best(atime.list)
## Compute and plot data size N for given time/memory.
pred.list <- predict(best.list, seconds=.01, kilobytes=100)
plot(pred.list)
```


```{r benchmark_base}
N <- 10
bm <- bench::mark(
  base_loop = uuid_v4_base_loop(N),
  base_vector = uuid_v4_base_vector(N),
  relative = T,
  check = F
)

bm

plot(bm)
```

Will opt for `uuid_v4_base_vector` implementation for base R.

```{r atime_comparison}
atime.list <- atime::atime(
  N = subject.size.vec,
  base = uuid_v4_base_vector(N),
  uuid = uuid::UUIDgenerate(n = N),
  uwu = uwu::new_v4(N),
  cpp = uuid_v4_cpp(N)
)


atime.list
plot(atime.list)
## Compute and plot asymptotic reference lines:
best.list <- atime::references_best(atime.list)
## Compute and plot data size N for given time/memory.
pred.list <- predict(best.list, seconds=.01, kilobytes=100)
plot(pred.list)
```


```{r benchmark_comparison}
N <- 10
bm <- bench::mark(
  base = uuid_v4_base_vector(N),
  uuid = uuid::UUIDgenerate(n = N),
  uwu = uwu::new_v4(N),
  cpp = uuid_v4_cpp(N),
  relative = T,
  check = F
)

bm

plot(bm)
```


## Summary:

It looks like the package `uwu` has the best performance. However I am really surprised in the base R implementation. It looks like it out performs the `uuid` package and only slightly slower than the c++ implementation.

## Session Information:

```{r sessioninfo}
sessioninfo::session_info()
```
